---
title: "Homework 3: p8105_hw3_ab4797.git"
author: "Ani Bilazarian"
date: "10/11/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
devtools:: install_github("p8105/p8105.datasets")
```

_ Import Instacart Data
```{r message=FALSE, warning=FALSE}
instacart_data = 
  library(p8105.datasets)
data("instacart") 
```

_ Clean & Import Data 

* Change Product Name to a factor variable
* Renaming variables

```{r}
instacart = 
  instacart %>% 
  janitor::clean_names() %>% 
  rename("order_cart" = add_to_cart_order, "day" = order_dow, "hour" = order_hour_of_day, "name" = product_name) %>% 
  mutate(name = as.factor(name))
```

_ Explore Data 

* The instacart dataset comes from an online grocery service with over 3 million online grocery orders from more than 200,000 Instacart users. This dataset allows us to observe trends in online grocery purchasing. The main variables are name (indicating the type of product), aisle (indicating which aisle the product came from) and the hour and day of the week that these items were ordered. Here are a variety of ways we can explore the data. With summmarize, we can observe the different types of products and how many people order. 

```{r}
instacart %>% 
  group_by(name) %>% 
  summarize(n= n())
```

_ Exploratory plot

* I started doing exploratory plots and saw quite quickly that the distribution of products ordered is extremely right skewed. There are by far fewer products that people order time and time again (> 5000) then items that are bought infrequently I wanted to identify which products are ordered by far the most. These are Bananas, Strawberries, Spinach, and other fruits and vegetables. 

```{r}
instacart %>% 
  count(name) %>% 
  filter(n > 5000) %>% 
  mutate(name = fct_reorder(name, n, .desc = TRUE)) %>% 
  ggplot (aes(x = name, y = n)) + coord_flip() + 
	  geom_bar(stat = "identity") + labs(title = "Plot of Items Ordered for each Aisle", x = "Aisle ", y = "number of orders")
```


_ Understanding average day and average hour of purchases

* Here we are looking at the product name and the average day and hour people are ordering products. For example, of 461 orders of 1% Lowfat Milk, the average day to buy was 2.7 and 13th hour. So people are buying milk at the middle of their days! That is approximately the same day and hour that pepole are buying 100 calorie per bag popcorn, interesting! 

```{r}
instacart %>% 
   group_by(name) %>% 
  summarize(n = n(),
            mean_hour = mean(hour, na.rm = TRUE), 
            mean_day = mean(day, na.rm = TRUE)
            ) %>% 
    mutate(product_ranking = min_rank(n))
```


_ Counting Aisles 

* Here we can see that there are 134 aisles. 

```{r}
instacart %>% 
count(aisle_id, aisle)
```

_ Which aisles are the most items ordered from? 

* Here we can see the top 5 aisles that items are ordered from. The aisles with the top purchases are "water seltzer sparkling water" and "yogurt". In fact, there are more purchases from the yogurt aisle then the last three combined! What does this mean for lactose intolerance. 

```{r}
instacart %>% 
  count(aisle) %>%
  filter(min_rank(desc(aisle)) < 6 )
```



_ Plot showing the number of items ordered in each aisle 

```{r making my plot pretty, message=FALSE}
library(ggridges)
library(patchwork)
library(viridis)

knitr::opts_chunk$set(
  echo = TRUE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

options(
  ggplot2.continuous.color = "viridis",
  ggplot2.continuous.fill = "viridis")

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_bw() + theme(legend.position = "bottom"))
```


```{r making the plot}
library(forcats)
instacart %>% 
  count(aisle) %>% 
  filter( n > 10000) %>% 
  mutate(aisle = fct_reorder(aisle, n, .desc = TRUE)) %>% 
  ggplot (aes(x = aisle, y = n)) + coord_flip() + 
	  geom_bar(stat = "identity") + labs(title = "Plot of Items Ordered for each Aisle", x = "Aisle ", y = "number of orders")
```


_ Table showing 3 most popular items in each of the aisles 

This table allows us to see the most popular items from three aisles. In the baking aisle the top products are 1) light brown sugar 2) baking soda and 3) cane sugar. In the vegetables/fruits aisle the top ingredients are 1) baby spinach 2) rasberries and 3) blueberries. In dog food care, the top products are 1) Snack Sticks 2) Organix Chicken, and 3) Small dog biscuits. 

```{r}
instacart %>% 
      filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
           group_by(aisle, name) %>% 
           summarize(n = n()) %>% 
           top_n(3) %>% 
           arrange(desc(n)) %>% 
          knitr::kable()
```

_ Table showing mean hour of the day when Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week

* We can see that the mean hour of the day most orders occur is between 12-15 indicating that people are online shopping at work!! 

```{r}
instacart %>% 
    mutate(day = recode(day,
                   '1' = "monday", 
                   '2' = "tuesday", 
                   '3' = "wednesday", 
                   '4' = "thursday", 
                   '5' = "friday",
                   '6' = "saturday", 
                   '0' = "sunday"))  %>% 
    filter(name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
    select(name, day, hour) %>% 
    group_by(name, day) %>% 
    summarise(mean_hour = round(mean(hour, na.rm = TRUE))) %>% 
    spread(key = day, value = mean_hour) %>% 
    knitr::kable()
```

# PROBLEM 2 


_ Importing BRFFS Data

```{r}
  library(p8105.datasets)
data("brfss_smart2010") 
```

# Problem 2 Cleaning
_ Clean BRFSS Data 

* I have cleaned the data here, renamed variables and organized just by "Overall Health." I changed my variable to be a factor vector, but my code won't run so I have attached it here. I have tried to sort and order but both won't work. 

+ sort.list(response, partial = NULL, na.last = TRUE, decreasing = FALSE, method = c("Poor", "Fair", "Good", "Very Good", "Excellent"))
 
 + order(oops_brfss_smart2010, response, na.last = TRUE, decreasing = FALSE, method = c("Poor", "Fair", "Good", "Very Good", "Excellent"))

```{r}
  library(p8105.datasets)
data("brfss_smart2010") 

  brfss_smart2010 = 
  brfss_smart2010 %>%  
  janitor::clean_names() %>% 
      rename(state = locationabbr, county = locationdesc) %>% 
        select(year:data_value) %>% 
  filter(topic == "Overall Health") %>% 
    filter(response == c("Poor", "Fair", "Good", "Very Good", "Excellent")) %>%
            mutate(response = as.factor(response))
```





